Replacing handwritten signatures with open electronic signature software

### 2020-05-18 paper/main.tex
Fix suggestions from tutor

With regards to electronic signatures, law within the EU used to differ, with the law applicable in the SR being now-repealed \textit{Act No. 215/2002 Coll.}. This situation changed with the EU Regulation eIDAS.

@@

As we have already mentioned, software licenses can influence whether and how it can be used as a part of different software.
Both when we are the ones using someone else's software and when someone else is using our software.
Generally speaking, the more open the license is, the higher the probability it will not prevent adoption for legal reasons.
We provide examples of categorized licenses in Figure \ref{fig:license-comparison}.

>>>>

Regarding the electronic signatures, law within the EU used to differ, with the law applicable in the SR being now-repealed \textit{Act No. 215/2002 Coll.}. This situation changed with the EU Regulation eIDAS.

@@

As we have already mentioned, software licenses can influence whether and how it can be used as a part of different software.
Both when we are the ones using someone else's software and when someone else is using our software.
Generally speaking, the more open the license is, the more likely it is it will not hinder adoption for legal reasons.
We provide examples of categorized licenses in Figure \ref{fig:license-comparison}.
